|

### 2018-06-15 Paper.Rmd
Stars and bars

---
title: | 
  | Campaign Contribution Limits and Corruption: 
  | Evidence from the 50 states
author: "Mark Hand"
date: "5/23/2018"
output: pdf_document
---

@@

```{r stargazer CCI latex, results="asis", eval=TRUE}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.

@@

```{r stargazer CRI latex, results="asis", eval=TRUE}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"))
```

The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels. As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index.

@@

```{r stargazer controlled panel latex, results="asis", eval=TRUE}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  title = "Are campaign limits and correlated with corruption convictions or reflections?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)")
  )
```

@@

```{r stargazer DiD latex, results="asis", eval=TRUE}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"))

>>>>

---
title: | 
  | Campaign Contribution Limits and Corruption: 
  | Evidence from the 50 states
author: "Mark Hand"
date: "5/23/2018"
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

@@

```{r stargazer CCI latex, results="asis", eval=TRUE}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,
  type="latex", 
  title = "Are campaign limits and corruption convictions correlated?",
  dep.var.labels = c("Corruption Convictions Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2)
```
\newpage
The second set of models (below) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.087 point decline in the Corruption Reflection Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), meaning that the presence of individual-to-party limits is associated with an 8.7% point decrease in the index.

@@

```{r stargazer CRI latex, results="asis", eval=TRUE}
stargazer(CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  title = "Are campaign limits and corruption reflections correlated?",
  dep.var.labels = c("Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2)
```

The third set of models incorporates a number of control variables in order to isolate the effect of campaign finance laws on corruption arrest levels. As in the models above, the only correlation significant at the p<0.05 level is the presence of limits on what an individual can give to a party; again, the presence of limits in what an individual can give to a party is associated with a decline in the Corruption Reflections Index. 
\newpage

@@

```{r 3 stargazer controlled panel latex, results="asis", eval=TRUE}
stargazer(CCIcontrol01,CCIcontrol02,CRIcontrol01,CRIcontrol02,
  title = "Are campaign limits and correlated with corruption convictions or reflections?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Divided government", "Binding one-term limit"," Binding two-term limit","Real per capita income (thousands)","AUSAs per million population","Unemployment","Citizen ideology measure","Percent high school graduates","Real per capita gov revenues (thousands)","Inequality: Male wages","Relative government wages","Urbanization","Log of population (millions)","Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  font.size = "small",
  header=FALSE,
  column.sep.width = "-15pt",
  no.space = T,
  digits = 2, digits.extra = 2)
```

@@

\newpage
\blandscape
```{r stargazer DiD latex, results="asis", eval=TRUE}
stargazer(CCIDID01, CCIDID02, CCIDID03, CRIDID01, CRIDID02, CRIDID03,
  title = "Do changes in limits lead to lower levels of corruption?",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limits removed","Individual limits imposed","Individual limit amount","Individual limits removed*amount","Individual limits imposed*amount",
                     "PAC limits removed","PAC limits imposed","PAC limit amount","PAC limits removed*amount","PAC limits imposed*amount",
                     "Individual-to-party limits removed","Individual-to-party limits imposed","Individual-to-party limit amount","Individual-to-party limits removed*amount","Individual-to-party limits imposed*amount"),
  font.size = "small", 
  header = FALSE,
  column.sep.width = "-15pt",
  digits = 2, digits.extra = 2,
  no.space = TRUE)

```
\elandscape
